ms_borrador

### 2018-01-23 man/ms_tables/t_robust_anovas.Rmd
formatted robust table

**Table 3.** Robust ANOVAS

@@

dff <- df %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Disturb", 
                           "disturb_year:site" = "Disturb X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Disturb", "Site", "Disturb X Site")))

@@

dff <- df %>% 
  filter(variables != "rrs") %>% 
  gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Disturb", 
                           "disturb_year:site" = "Disturb X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Disturb", "Site", "Disturb X Site")))

>>>>

**Table 3.** Robust two-way ANOVAs of the resilience metrics of greenness (EVI) and tree-growth (BAI) for the factor drought events (2005 and 2012) and site.

@@

dff <- df %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drougth event", 
                           "disturb_year:site" = "Drougth event X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drougth event", "Site", "Drougth event X Site")))

@@

dff <- df %>% 
  filter(variables != "rrs") %>% 
  gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drougth event", 
                           "disturb_year:site" = "Drougth event X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drougth event", "Site", "Drougth event X Site")))
